\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-24 manuscript.Rnw
Perform subgroup analysis in PSM example

<<psm_hesim_data>>=
hesim_dat$patients <- data.table(
  patient_id = 1:4,
  grp_id = c(1, 1, 0, 0),
  patient_wt = rep(1/4, 4),
  age = c(55, 65, 55, 65),
  female = c(1, 1, 0, 0)
)
@

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize()
cea_pw_psm <- cea_pw(ce_sim_psm, comparator = 1,
                     dr_qalys = .03, dr_costs = .03)
icer_tbl(cea_pw_psm, colnames = strategies$strategy_name,
         k = 100000)
@

>>>>

<<psm_hesim_data>>=
hesim_dat$patients <- data.table(
  patient_id = 1:4,
  grp_id = c(1, 1, 2, 2),
  patient_wt = rep(1/4, 4),
  age = c(55, 65, 55, 65),
  female = c(1, 1, 0, 0)
)
@

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
cea_pw_psm <- cea_pw(ce_sim_psm, comparator = 1,
                     dr_qalys = .03, dr_costs = .03)
icer_tbl(cea_pw_psm, output = "data.table",
         k = 100000)
@
